5'CutSiteAnalysisDataGeneration

### 2022-12-06 R/5'CutSiteAnalysisDataGeneration.rmd
Fixed a bug involving a misnamed variable

  if (alsoCreateSequenceLogoInput) {
    write(str_sub(readData$Read_Sequence, 1, 17), sep = '\n', file = generateFilePath(
      directory, dataTypeStrings$sequenceLogoInput, ".txt",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, strandPolarity = FIVE_PRIME, filtering = filtering
    ))
    write(str_sub(readData$Read_Sequence, -14, -1), sep = '\n', file = generateFilePath(
      generalReadSequenceDataDirectory, dataTypeStrings$sequenceLogoInput, ".txt",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, strandPolarity = THREE_PRIME, filtering = filtering
    ))
  }

>>>>

  if (alsoCreateSequenceLogoInput) {
    write(str_sub(readData$Read_Sequence, 1, 17), sep = '\n', file = generateFilePath(
      directory, dataTypeStrings$sequenceLogoInput, ".txt",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, strandPolarity = FIVE_PRIME, filtering = filtering
    ))
    write(str_sub(readData$Read_Sequence, -14, -1), sep = '\n', file = generateFilePath(
      directory, dataTypeStrings$sequenceLogoInput, ".txt",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, strandPolarity = THREE_PRIME, filtering = filtering
    ))
  }
